Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-11-07 Milestone_1/01-chap1.Rmd
clean up repo

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, cache=TRUE, warning = FALSE)
# Load any R packages you need here
library(tidyverse)
library(visage)
```

@@

Online machine learning is a technique to train machine learning model with data arriving in a sequential order. Models trained with online learning can be updated immediately for any new arrival data, which overcomes the drawbacks of the traditional batch learning where training data required to be available prior to the training. It is suitable for large-scale machine learning tasks in real-world data analytics applications [@].

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, cache=TRUE, warning = FALSE)
# Load any R packages you need here
library(tidyverse)
library(bandicoot)
library(visage)
```

@@

Online machine learning is a technique to train machine learning model with data arriving in a sequential order. Models trained with online learning can be updated immediately for any new arrival data, which overcomes the drawbacks of the traditional batch learning where training data required to be available prior to the training. It is suitable for large-scale machine learning tasks in real-world data analytics applications [@hoi_online_2018].
